---
title: "Anthony_Tidyverse"
author: "Anthony Munoz"
date: "5/5/2019"
output: html_document
---



## Introduction 

Data 607 Assigment 
Tidyverse package.
I will be choosing the following libraries from tydiverse
ggplot
dplyr
tidyr
readr

The data for this assignment was download from https://www.kaggle.com/gregorut/videogamesales


```{r warning=FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readr)
```

## Data loading

#read_csv()
use the function to read a csv file into a varible 
```{r}

vg.data <- read_csv("vgsales.csv")


```


## data wrangling with tydeverse libraries tidyr and dplyer


on this part i will be working with tidyr and dplyer libraries in order to split/organize/summarize the data

# select()
# summarise()
#group_by()
```{r}

data.north.america <- vg.data %>% select(Name,Platform,Year,Genre,Publisher,NA_Sales) 
data.EU <- vg.data %>% select(Name,Platform,Year,Genre,Publisher,EU_Sales) 
data.JP <- vg.data %>% select(Name,Platform,Year,Genre,Publisher,JP_Sales) 



genre.total.category <- vg.data %>% group_by(Genre) %>% summarise(total = n())
head(genre.total.category)

```
## Graph ggplot


```{r}
# graph showing the Genre game by total count on a bar plot
gplot <- ggplot(genre.total.category, aes(x=Genre, y=total)) + geom_bar(stat = "identity")

gplot




```